---
title: "FARS data package"
author: "Rafael Garcia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package can be used to read and manage data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

## Importing data

FARS data can be imported using the `fars_read_years` function:

```{r read}
library(fars)
fars_data <- fars_read(make_filename(2014))
```

This file contains many information regarind the traffic accidents. The fields contained in the dataframe are

```{r sample}
library(magrittr)
library(knitr)
fars_data %>%
  names() %>%
  kable(col.names = 'Columns')
``` 

## Other usages

The package also contains functions for calculating the summary for a set of years:

```{r summary}
fars_summarize_years(2013:2015) %>%
  kable()
```

And also the capability of plotting data into a map. In this case, the State is to be selected by the State ID.



For the case of California (ID = 6)

```{r map}
fars_map_state(6, 2015)
```

For the case of New York (ID 36)

```{r map2}
fars_map_state(36, 2015)
```
